---
title: '<span style="font-size: 110%;">R</span><span style="font-size:100%">2D2</span>  <span style="font-size:55%"><i>[and friends]</span>'
subtitle: '<em>TO THE RESCUE</em>'
output: 
  html_document:
    css: "glow.css"
---

```{r, include=F}
#Colors: https://mn.gov/portal/brand/style-guide/colors/
```

<br><br>
<style>

@import url('https://fonts.googleapis.com/css2?family=Montserrat&display=swap');
@import url('https://fonts.googleapis.com/css2?family=Poller+One&display=swap');

@import url('https://fonts.googleapis.com/css2?family=Audiowide&display=swap&text=R2D2SAVESTHEDAY');

body {
  background-color:   #f1e0c4; /*#008EAA; #f5f5f5 #222d32 */
  font-family: 'Montserrat', sans-serif;
  font-size: 11px;
  width: 1600px;
  height: 1000px;
}

h1.title {
  font-family: 'Audiowide', 'Poller One', 'Montserrat', sans-serif;
  font-size: 72px;
  color:  white;  /*#f9d71c; #F8E81C; #220e0f; #CEB67E;*/
  margin-top: 12px;
  margin-left: -252px;
}

h2 {
   text-align: left;
   margin-top: -2px;
   margin-bottom: 8px;
   font-weight: bold;
   font-size: 120%;
   color:  #008EAA;  /*#003865; */
}

.subtitle {
  font-family: 'Audiowide', 'Poller One', 'Montserrat', sans-serif;
  font-size: 44px;
  color:  white;  /*#f9d71c; #F8E81C; #220e0f; #CEB67E;*/
  margin-top: -12px;
  margin-left: -252px;
}

.div1 {
  position: absolute;
  height: 350px;
  width: 800px;
  margin-left: 60px;
  /*border: 1px solid gray;*/
  perspective: 500px;
}

.card-out {
  position: absolute;
  height: 350px;
  width: 600px;
  margin-left: 60px;
  /*border: 1px solid gray;*/
  perspective: 500px;
}

.div2 {
  transform-style: preserve-3d;
  transform: rotateX(35deg);
}

.card {
  width: 138px;
  min-height: 200px;
  max-height: 200px;
  margin-top: 0;
  margin-left: 0;
  border-radius: 8px;
  position: absolute;
  left: 34px; 
  top: 280px;
  border: solid 2px #eee; /*#003865; */
  box-shadow: 0 3px 5px 0 rgba(0,0,0,0.2); 
  background-color: white; /*#e3d2b6;*/
  overflow: hidden;
}

.short {
  min-height: 70px;
  max-height: 160px;
}

.shortcard {
  max-height: 75px;
}


.gray {
  color: #444458e0;
}

h2.gray {

  color: #31464a88;
}

.card:hover {
  border: inherit;
  box-shadow: 0 5px 6px 0 rgba(0,0,0,0.3); 
}

.card.gray:hover {
  border: inherit;
  box-shadow: inherit;
}

.closed {
  background-color: #676666;
  font-family: 'Poller One';
}

.top-card {
  overflow: hidden;
  max-height: 80px;
  border-radius: 6px 6px 0 0;
  margin-bottom: 10px;
  border-bottom: solid 2px #eee;
}

.bottom-card {
  padding: 9px;
  padding-top: 5px;
  padding-bottom: 0;
  overflow: hidden;
  width: 100%;
}

img {
  margin-top: 0px;
  margin-bottom: 0px;
  width: 100%;
}

.lildot {
  height: 90px;
  width: 90px;
  position: absolute;
  border-radius: 50%;
  display: inline-block;
  border: solid 9px #e3d2b6;
}

.bigdot {
  height: 210px;
  width: 210px;
}

.planet {
  height: 55px;
  width: 55px;
}

.labels {
  position: absolute;
  font-size: 20px;
  font-weight: 800;
  /*background-color: white; #e3d2b6;*/
  border-radius: 3px;
  padding: 6px;
  padding-right: 7px;
}

.player {
  font-size: 12px;
  height: 21px;
  color: black;
  padding: 3px;
  padding-right: 5px;
}

.lines {
  position: absolute;
  width: 110px;
  height: 4px;
  background-color: #cecd97;
  z-index: -1200;
}

.jedi {
  height: 5px;
  background-color: #f0f7f7; 
  border: 2px solid #3fb9e9;
}

.dashed {
  background-color: #f1e0c4;
  border-bottom: 3px dashed #cecd97;
}

.dotted {
  background-color: #f1e0c4;
  border-bottom: 3px dotted #9a9a7cc7;
}

.vline {
  position: absolute;
  width: 2px;
  height: 30px;
  background-color: #888;
}

.footnote {
  font-size: 11px;
  margin-top: 800px;
  text-align: right;
  margin-left: 200px;
}


a, a:active, a:hover, a:visited {
  text-decoration: none;
  color: inherit;
}

</style>
  
  
```{r, include=F}
library(icon)

source("/home/dk/Desktop/new/skills_map/R/cards_html.R")
```

<span style="color: #f1e0c4;">`r icon::fa("lock")`</span>

<div class="saber"></div>

<div class="vline dotted" style="left: 386px; top: 494px; height: 87px; border-left: 3px dotted #9a9a7cc7; background-color: #f1e0c4;"></div>
<div class="lines dotted" style="left: 386px; top: 537px; width: 248px;"></div>
<div class="vline dotted" style="left: 633px; top: 428px; height: 107px; border-left: 3px dotted #9a9a7cc7; background-color: #f1e0c4;"></div>

<div class="vline dotted" style="left: 634px; top: 113px; height: 126px; border-left: 3px dotted #9a9a7cc7; background-color: #f1e0c4;"></div>
<div class="lines dotted" style="left: 640px; top: 162px; width: 174px;"></div>
 
<div class="vline dotted" style="left: 924px; top: 292px; height: 75px; border-left: 3px dotted #9a9a7cc7; background-color: #f1e0c4;"></div>
 
<div class="lines jedi" style="left: 902px; top: 807px;"></div>
 
<span class="lildot saber" style="left: 110px; top: 360px;  border: solid 2px #cecd97; background-color: white; /*#cecd97;*/"></span>
<div class="labels" style="left: 117px; top: 386px; color: #736b69;">
<a href="https://github.com/MPCA-data/tidytuesdays/blob/master/show-n-tell/R2D2_tracker/stage_0.MD#start-here">START</a>
</div>


```{r, results="asis", echo=F}
# Wampa
add_card(n = 1, left=317, top=290, text='Find the right <b> time </b> to rescue Luke!', is_linked = F)

# TaunTaun
add_card(n = 1, left=317, top=584, text='', title="TAUNTAUN RACE ", image="/home/dk/Pictures/tauntaun.png", shortcard = T, gray = T)

#AT-AT
add_card(n = 2, left=573, top=222, title="AT-AT INTERFERENCE", text='Uncover the radio frequency hidden in <em> Excel </em>...', image = "/home/dk/Pictures/at-at.png", expand = "124%", vjust=0, is_linked=F, gray=T)

# Yoda
add_big_circle(top=76, left=820, image="/home/dk/Pictures/yoda.png", color="#d3b68e", planet_color="#925f28")

# Locked level
add_locked_card(left=856, top=370)

add_player(left=129, top=344, p_name="R2D2", color="#c4e60a9c", flip=T)
add_player(left=96, top=334, p_name="MiMi", color="#371ba285", flip=T)
add_player(left=44, top=352, p_name="KMEL", color="#1ad45985", flip=T)
add_player("bb8", left=88, top=406, p_name="DNAG", color="#e47917b3", width = 37, layer = 104)

#add_spinner()
```

<br><br><br>

<p class="footnote">
_&#174; This project funded by a generous grant from the Galactic Empire_
</p> 

